\mytitle

### 2012-03-08 papers/SAS2012/implicitization.tex
nouveaux chiffres

\begin{figure}[h!]
      \centering
      \begin{tabular}{|l|r|r|r|r|r|r|r|} \hline
        \multicolumn{1}{|c|}{} &
        \multicolumn{2}{c|}{Size} &
        \multicolumn{5}{c|}{Execution time (seconds)} \\ \hline
        \multicolumn{1}{|c|}{Name} & 
        \multicolumn{1}{c|}{kLOC}  & 
        \multicolumn{1}{c|}{$|P_R|$}  &
        \multicolumn{1}{c|}{\textbf{S}} &
        \multicolumn{1}{c|}{\textbf{G}} &
        \multicolumn{1}{c|}{\textbf{PF}} &
        \multicolumn{1}{c|}{\textbf{G+PF}} &
	\multicolumn{1}{c|}{\textbf{DIS}} \\ 
        \hline
        % M-x align RET powers ;-).
a2ps-4.14      & 55  & 2012  & 64  & 17  & 66   & 175  & 512   \\
gawk-4.0.0     & 59  & 902   & 59  & 8   & 18   & 43   & 129   \\
gnuchess-6.0.0 & 38  & 1222  & 112 & 21  & 122  & 374  & 866   \\
gnugo-3.8      & 83  & 2801  & 155 & 31  & 128  & 382  & 1403  \\
grep-2.9       & 35  & 820   & 50  & 12  & 21   & 58   & 307   \\
gzip-1.4       & 27  & 494   & 63  & 12  & 36   & 97   & 617   \\
lapack-3.3.1   & 954 & 16422 & 721 & 246 & 2690 & 6052 & 22222 \\
make-3.82      & 34  & 993   & 22  & 7   & 32   & 83   & 255   \\
sed-4.2        & 23  & 292   & 35  & 7   & 23   & 69   & 521   \\
tar-1.26       & 73  & 1712  & 270 & 39  & 110  & 304  & 1164  \\
% TODO: mettre à jour les chiffres ?
	\hline
      \end{tabular}
      \label{fig:projects}

>>>>

\begin{figure}[h!]
      \centering
      \begin{tabular}{|l|r|r|r|r|r|r|r|} \hline
        \multicolumn{1}{|c|}{} &
        \multicolumn{2}{c|}{Size} &
        \multicolumn{5}{c|}{Execution time (seconds)} \\ \hline
        \multicolumn{1}{|c|}{Name} & 
        \multicolumn{1}{c|}{kLOC}  & 
        \multicolumn{1}{c|}{$|P_R|$}  &
        \multicolumn{1}{c|}{\textbf{S}} &
        \multicolumn{1}{c|}{\textbf{G}} &
        \multicolumn{1}{c|}{\textbf{PF}} &
        \multicolumn{1}{c|}{\textbf{G+PF}} &
	\multicolumn{1}{c|}{\textbf{DIS}} \\ 
        \hline
        % M-x align RET powers ;-).
		\input{table_time}
	\hline
      \end{tabular}
      \label{fig:projects}
